Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-25 paper/paper.tex
Iterate section 5

Figure~\ref{fig:read-write-transaction} illustrates the timeline of a distributed
read-write transaction. There are three participants groups involved, i.e., $P_2$,
$P_3$ and $P_{CL}$ (which is the coordinator leader). In the first step, all three
participants acquire their locks and execute $TT.now()$ right afterwards to obtain
timestamps independently. Every participant logs his timestamp through Paxos and
after this was done, sends its timestamp to the coordinator leader. The
coordinator leader then computes an overall timestamp for the transaction. This
timestamp must be greater than any timestamp the leader has assigned before,
greater or equal to all timestamps received from the participants and greater than
$TT.now().latest$ at the time the coordinator leader received the commit message.
Then, the computed timestamp is logged by the coordinator leader through Paxos
but no participants are notified until the commit wait rule is satisfied. After
commit wait is satisfied, the coordinator leader notifies all other participants
which are allowed to release their locks after receiving this notification.

@@

Table~\ref{tbl:performance-of-operations} summarizes the latency and throughput
performance of Spanner. 1D means one replica with Commit Wait disabled. Hence,
only write transactions are evaluated because Commit Wait is not involved in any
other type of transaction. As we can see, the latency of all transaction types is
almost stable for an increasing number of replicas whereas the standard deviation
decreases. The throughput of read-only transactions increases with the number of
replicas because the number of spanservers increases. In the experiments, the
number of replicas and the number of spanservers were equal. The throughput of write
transactions also benefits from this fact. However, the number of write operations
to perform increases linearly with the number of replicas. This explains why the
throughput of write transactions does not increase with the number of replicas.
Snapshot reads benefit the most from the Spanner architecture. The throughput of
snapshot reads increases almost linearly with the number of replicas.

>>>>

Figure~\ref{fig:read-write-transaction} illustrates the timeline of a distributed
read-write transaction. There are three participants groups involved: $P_2$, $P_3$
and $P_{CL}$ (which is the coordinator leader). In the first step, all three
participants acquire their locks and execute $TT.now()$ right afterwards to obtain
timestamps independently. Every participant logs his timestamp through Paxos and
after this was done, sends its timestamp to the coordinator leader. The
coordinator leader then computes an overall timestamp for the transaction. This
timestamp must be greater than any timestamp the leader has assigned before,
greater or equal to all timestamps received from the participants and greater than
$TT.now().latest$ at the time the coordinator leader received the commit message.
Then, the computed timestamp is logged by the coordinator leader through Paxos
but no participants are notified until the commit wait rule is satisfied. After
commit wait is satisfied, the coordinator leader notifies all other participants
which are allowed to release their locks after receiving this notification.

@@

Table~\ref{tbl:performance-of-operations} summarizes the latency and throughput
performance of Spanner. 1D means one replica with Commit Wait disabled. Hence,
only write transactions are evaluated because Commit Wait is not involved in any
other type of transaction. As we can see, the latency of all transaction types is
almost stable for an increasing number of replicas whereas the standard deviation
decreases. The throughput of read-only transactions increases with the number of
replicas because the number of spanservers increases. In the experiments, the
number of replicas and the number of spanservers were equal. The throughput of
write transactions also benefits from this fact. However, the number of write
operations to be performed increases linearly with the number of replicas. This
explains why the throughput of write transactions does not increase with the
number of replicas. Snapshot reads benefit the most from the Spanner architecture.
The throughput of snapshot reads increases almost linearly with the number of
replicas.
